Untitled

### 2021-04-14 production/analysis.Rmd
Se omitieron variables de control en los screenreg

# Resumen
screenreg(list(m1, m2, m3, m4), custom.model.names = c("soc. familiar", "recursos", "soc. escolar", "completo"), omit.coef = "(factor(sexo))|(factor(dependencia))|(factor(region))")

@@

screenreg(list(m4, m8, m9), custom.model.names = c("completo", "r_educ", "r_libros"), omit.coef = "(factor(sexo))|(factor(dependencia))|(factor(region))")

screenreg(list(m4, m5, m5b, m5c, m6, m6b, m6c), custom.model.names = c("completo", "r_conv", "aper x conv", "act x conv", "r_voto", "aper x voto", "act x voto"), omit.coef = "(factor(sexo))|(factor(dependencia))|(factor(region))")

htmlreg(l = m4, type = "html", doctype = FALSE)
```

@@

#Tabla de regresiones
screenreg(list(d1, d2, d3, d4), custom.model.names = c("soc. familiar", "recursos", "soc. escolar", "completo"), omit.coef = "(factor(sexo))|(factor(dependencia))|(factor(region))")

@@

screenreg(list(d4, d5, d6, d6b, d6c), custom.model.names = c("completo", "r_conv", "r_marcha", "marcha x conversacion", "marcha x apertura"), omit.coef = "(factor(sexo))|(factor(dependencia))|(factor(region))")

@@

screenreg(list(d4, d8, d9), custom.model.names = c("completo", "r_educ", "r_libros"), omit.coef = "(factor(sexo))|(factor(dependencia))|(factor(region))")
```

@@

screenreg(list(n1, n2, n3, n4), custom.model.names = c("soc. familiar", "recursos", "soc. escolar", "completo"), omit.coef = "(factor(sexo))|(factor(dependencia))|(factor(region))")

@@

screenreg(list(n4, n5, n6, n6a, n6b), custom.model.names = c("completo", "r_conv", "r_marcha", "marcha x conversacion", "marcha x apertura"), omit.coef = "(factor(sexo))|(factor(dependencia))|(factor(region))")

@@

screenreg(list(n4, d8, d9), custom.model.names = c("completo", "r_educ", "r_libros"), omit.coef = "(factor(sexo))|(factor(dependencia))|(factor(region))")
```

>>>>

# Resumen
screenreg(list(m1, m2, m3, m4), custom.model.names = c("soc. familiar", "recursos", "soc. escolar", "completo"), omit.coef = "sexo|dependencia|region")

@@

screenreg(list(m4, m8, m9), custom.model.names = c("completo", "r_educ", "r_libros"), omit.coef = "sexo|dependencia|region")

screenreg(list(m4, m5, m5b, m5c, m6, m6b, m6c), custom.model.names = c("completo", "r_conv", "aper x conv", "act x conv", "r_voto", "aper x voto", "act x voto"), omit.coef = "sexo|dependencia|region")
```

@@

#Tabla de regresiones
screenreg(list(d1, d2, d3, d4), custom.model.names = c("soc. familiar", "recursos", "soc. escolar", "completo"), omit.coef = "sexo|dependencia|region")

@@

screenreg(list(d4, d5, d6, d6b, d6c), custom.model.names = c("completo", "r_conv", "r_marcha", "marcha x conversacion", "marcha x apertura"), omit.coef = "sexo|dependencia|region")

@@

screenreg(list(d4, d8, d9), custom.model.names = c("completo", "r_educ", "r_libros"), omit.coef = "sexo|dependencia|region")
```

@@

screenreg(list(n1, n2, n3, n4), custom.model.names = c("soc. familiar", "recursos", "soc. escolar", "completo"), omit.coef = "sexo|dependencia|region")

@@

screenreg(list(n4, n5, n6, n6a, n6b), custom.model.names = c("completo", "r_conv", "r_marcha", "marcha x conversacion", "marcha x apertura"), omit.coef = "sexo|dependencia|region")

@@

screenreg(list(n4, d8, d9), custom.model.names = c("completo", "r_educ", "r_libros"), omit.coef = "sexo|dependencia|region")
```

### 2021-04-14 production/analysis_red.Rmd
Se omitieron variables de control en los screenreg

#BDD
load(url("https://github.com/damiranda/pol_parti/blob/branch1/input/data/proc/data.RData?raw=true"))

@@

# Resumen
screenreg(list(m1, m2, m3, m4), custom.model.names = c("soc. familiar", "recursos", "soc. escolar", "completo"), omit.coef = "(factor(sexo))|(factor(dependencia))|(factor(region))")

@@

screenreg(list(m4, m8, m9), custom.model.names = c("completo", "r_educ", "r_libros"), omit.coef = "(factor(sexo))|(factor(dependencia))|(factor(region))")

screenreg(list(m4, m5, m5b, m5c, m6, m6b, m6c), custom.model.names = c("completo", "r_conv", "aper x conv", "act x conv", "r_voto", "aper x voto", "act x voto"), omit.coef = "(factor(sexo))|(factor(dependencia))|(factor(region))")

htmlreg(l = m4, type = "html", doctype = FALSE)
```

@@

#Tabla de regresiones
screenreg(list(d1, d2, d3, d4), custom.model.names = c("soc. familiar", "recursos", "soc. escolar", "completo"), omit.coef = "(factor(sexo))|(factor(dependencia))|(factor(region))")

@@

screenreg(list(d4, d5, d6, d6b, d6c), custom.model.names = c("completo", "r_conv", "r_marcha", "marcha x conversacion", "marcha x apertura"), omit.coef = "(factor(sexo))|(factor(dependencia))|(factor(region))")

@@

screenreg(list(d4, d8, d9), custom.model.names = c("completo", "r_educ", "r_libros"), omit.coef = "(factor(sexo))|(factor(dependencia))|(factor(region))")
```

@@

screenreg(list(n1, n2, n3, n4), custom.model.names = c("soc. familiar", "recursos", "soc. escolar", "completo"), omit.coef = "(factor(sexo))|(factor(dependencia))|(factor(region))")

@@

screenreg(list(n4, n5, n6, n6a, n6b), custom.model.names = c("completo", "r_conv", "r_marcha", "marcha x conversacion", "marcha x apertura"), omit.coef = "(factor(sexo))|(factor(dependencia))|(factor(region))")

@@

screenreg(list(n4, d8, d9), custom.model.names = c("completo", "r_educ", "r_libros"), omit.coef = "(factor(sexo))|(factor(dependencia))|(factor(region))")
```

>>>>

#BDDb
load(url("https://github.com/damiranda/pol_parti/blob/branch1/input/data/proc/data.RData?raw=true"))

@@

# Resumen
screenreg(list(m1, m2, m3, m4), custom.model.names = c("soc. familiar", "recursos", "soc. escolar", "completo"), omit.coef = "(sexo|dependencia|region)")

@@

screenreg(list(m4, m8, m9), custom.model.names = c("completo", "r_educ", "r_libros"), omit.coef = "(sexo|dependencia|region)")

screenreg(list(m4, m5, m5b, m5c, m6, m6b, m6c), custom.model.names = c("completo", "r_conv", "aper x conv", "act x conv", "r_voto", "aper x voto", "act x voto"), omit.coef = "(sexo|dependencia|region)")
```

@@

#Tabla de regresiones
screenreg(list(d1, d2, d3, d4), custom.model.names = c("soc. familiar", "recursos", "soc. escolar", "completo"), omit.coef = "(sexo|dependencia|region)")

@@

screenreg(list(d4, d5, d6, d6b, d6c), custom.model.names = c("completo", "r_conv", "r_marcha", "marcha x conversacion", "marcha x apertura"), omit.coef = "(sexo|dependencia|region)")

@@

screenreg(list(d4, d8, d9), custom.model.names = c("completo", "r_educ", "r_libros"), omit.coef = "(sexo|dependencia|region)")
```

@@

screenreg(list(n1, n2, n3, n4), custom.model.names = c("soc. familiar", "recursos", "soc. escolar", "completo"), omit.coef = "(sexo|dependencia|region)")

@@

screenreg(list(n4, n5, n6, n6a, n6b), custom.model.names = c("completo", "r_conv", "r_marcha", "marcha x conversacion", "marcha x apertura"), omit.coef = "(sexo|dependencia|region)")

@@

screenreg(list(n4, d8, d9), custom.model.names = c("completo", "r_educ", "r_libros"), omit.coef = "(sexo|dependencia|region)")
```
